\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Discussion: Limits

Such recurrent activity would be essential for implementing predictive or anticipatory processes. This is essential in a neural system as it contains multiple different delays that require temporal alignment~\citep{hogendoorn_predictive_2019}. This has been previously modeled to explain for example the flash-lag illusion~\citep{khoei_flash-lag_2017}. As previously stated ".... "~\citep{perrinet_active_2014}, and our hetero-synaptic model would provide a simple and elegant solution to this problem.

>>>>

Such recurrent activity would be essential for implementing predictive or anticipatory processes. This is essential in a neural system as it contains multiple different delays that require temporal alignment~\citep{hogendoorn_predictive_2019}. This has been previously modeled to explain for example the flash-lag illusion~\citep{khoei_flash-lag_2017}. As previously stated, this could be implemented using generalized coordinates (position, speed, acceleration, ...) and ``neurobiologically, the application of delay operators just means changing synaptic connection strengths to take different mixtures of generalized sensations and their prediction errors''~\citep{perrinet_active_2014}. Our proposed hetero-synaptic model provides an alternate elegant solution to this problem.
